The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-07-20 paper2_JNLS/paper.tex
NM

>>>>

	As discussed in \cite{bolles2019anomalous}, the experiments consist of a long, narrow wave tank (6 m long x 20 cm wide x 30 cm high), with waves generated by plexiglass paddle at one end. The waves propagate through the tank and, roughly midway through, pass over an abrupt depth change (ADC), which is created by a plexiglass step. The waves continue to propagate through the shallower depth until reaching the far end of the tank, at which point their energy is dissipated by a horse-hair dampener. Since this dampener minimizes the backscatter, the waves propagate primarily in one direction only, from left to right in Fig.~\ref{fig1}. The free surface is illuminated by light-emitting diodes that run along the bottom of the tank and imaged from the sideview with a Nikon D3300 at 60 frames per second. This arrangement allows measurements of surface displacements with a precision of 1/3 millimeter.

 % Figure 1
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.85 \linewidth]{Figs/fig1.pdf}
\caption{
(a) Experimental schematic. Reproduced from \cite{bolles2019anomalous}
}
%(b)--(c) Surface displacement measured at a representative upstream and downstream location. (d)--(e) Corresponding histograms.
\label{fig1}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

 % Figure 2
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.85 \linewidth]{Figs/fig2.pdf}
\caption{
(b)--(c) Surface displacement measured at a representative upstream and downstream location. (d)--(e) Corresponding histograms. Reproduced from \cite{bolles2019anomalous}
}
\label{fig1}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 % Data from column 5 in MasterTimeSeries, Delta theta = 1.38 degrees

  % Figure 3
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.85 \linewidth]{Figs/fig3.pdf}
\caption{
(b)--(c) Surface slope measured at a representative upstream and downstream location. (d)--(e) Corresponding histograms. NEW PLOT.
}
\label{fig1}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
